### 2013-09-16 chi2014/introduction.tex
citations and some figure markup

Brainstorming is a tool proposed by Osborne [CITE] that has achieved widespread popularity and similarly widespread research and controversy. Brainstorming methods have been applied in many scenarios, from spatially co-located participants to electronic brainstorming over computer networks [CITE]. The introduction of crowd marketplaces such as Amazon's Mechanical Turk [CITE] and the corresponding paradigm of massively parallel Human Intelligence Tasks provide both a natural venue to solicit ideas and a new context in which to establish models of brainstorming activity.

@@

In the course of their research in Human-Computer Interactions, two of the authors went looking for these sets of guidelines to apply them to a crowd idea generation task. While previous work has utilized brainstorming techniques in crowd marketplaces [CITE], we were unable to find any generalizable models or guidelines for brainstorming in the context of the crowd. Models such as Nijstaf and Stroebe's SIAM [CITE] make and test predictions regarding in-person brainstorming, but we did not find similar baselines for electronic or crowd brainstorming.

@@

Furthermore, we examine predictions made by Nijstaf and Stroebe's model of in-person brainstorming and test them in the context of crowd brainstorming. We find that the tested predictions hold: that ideas generated in sequence tend to belong to the same category, and that the time spent to generate when changing categories is signficantly greater than when generating ideas within the same category.

>>>>

Brainstorming is a tool proposed by Osborne \cite{osborn_applied_1957} that has achieved widespread popularity and similarly widespread research and controversy. Brainstorming methods have been applied in many scenarios, from spatially and temporally co-located participants to electronic brainstorming over computer networks \cite{pinsonneault_electronic_1999}. The introduction of crowd marketplaces such as Amazon's Mechanical Turk \cite{_amazon_????} and the corresponding paradigm of massively parallel Human Intelligence Tasks provide both a natural venue to solicit ideas and a new context in which to establish models of brainstorming activity.

@@

In the course of their research in Human-Computer Interactions, two of the authors went looking for these sets of guidelines to apply them to a crowd idea generation task. While previous work has utilized brainstorming techniques in crowd marketplaces [CITE], we were unable to find any generalizable models or guidelines for brainstorming in the context of the crowd. Models such as Nijstaf and Stroebe's SIAM \cite{nijstad_how_2006} make and test predictions regarding in-person brainstorming, but we did not find similar baselines for electronic or crowd brainstorming.

@@

Furthermore, we examine predictions made by Nijstad and Stroebe's model of in-person brainstorming and test them in the context of crowd brainstorming. We find that the tested predictions hold: that ideas generated in sequence tend to belong to the same category, and that the time spent to generate when changing categories is signficantly greater than when generating ideas within the same category.

### 2013-09-16 chi2014/method.tex
citations and some figure markup

Participants were recruited from Amazon's \emph{Mechanical Turk} (CITE), and were restricted to residents of the United States for a baseline expectation of english language comprehension and cultural familiarity. Mechanical Turk is an online marketplace in which members receive financial reward for completing \emph{Human Intelligence Tasks}, or HITs.

@@

At the beginning of the form is a brief introduction to brainstorming, with a paraphrase of Osborne's four rules of brainstorming (CITE). These rules were manipulated to make sense within the constraints nominal brainstorming over the web medium. The rules, as displayed to the participants:

@@

With this basic design in hand, we ran several pilots and experiments. In early pilots, we used classic problems from psychology literature on brainstorming, including the "thumb problem" and "broom problem" (CITE). Early results from brainstormers were unsatisfying and wildly divergent. We identified three key traits problems needed in order to evaluate them for creativity:

@@

An \emph{instance} is a single response by a single participant to a brainstorming question. For example, Figure FIG gives four \emph{instances} provided in the \emph{MP3 player} brainstorming task.

\begin{figure}[!h]
    \begin{enumerate}
        \item "Use as a mirror"
        \item "Mirror"
        \item "Use it as a mirror for makeup"
        \item "Tape it to a telephone pole and use as a reflector"
    \end{enumerate}
\end{figure}

@@

The clustering algorithm is described in Figure FIG. Instances are added one at a time to the existing idea forest. In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

@@

As our measure of originality, we use \emph{o-score}, introduced by Jansson and Smith [CITE]. An idea's o-score is $1 - p(idea)$, where $p(idea) = (number of instances of that idea)/(number of instances total)$. We similarly calculate o-score for categories. Throughout this paper, we will occasionally refer to the \emph{category o-score} of an idea. This simply refers to the o-score of the category tree to which that idea belongs.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{idea_height}
\end{figure}

>>>>

Participants were recruited from Amazon's \emph{Mechanical Turk} \cite{_amazon_????}, and were restricted to residents of the United States for a baseline expectation of english language comprehension and cultural familiarity. Mechanical Turk is an online marketplace in which members receive financial reward for completing \emph{Human Intelligence Tasks}, or HITs.

@@

At the beginning of the form is a brief introduction to brainstorming, with a paraphrase of Osborne's four rules of brainstorming \cite{osborn_applied_1957}. These rules were manipulated to make sense within the constraints nominal brainstorming over the web medium. The rules, as displayed to the participants:

@@

With this basic design in hand, we ran several pilots and experiments. In early pilots, we used classic problems from psychology literature on brainstorming, including the "thumb problem" and "broom problem" \cite{isaksen_review_1997}. Early results from brainstormers were unsatisfying and wildly divergent. We identified three key traits problems needed in order to evaluate them for creativity:

@@

An \emph{instance} is a single response by a single participant to a brainstorming question. For example, figure~\ref{fig:sample_instances} gives four \emph{instances} provided in the \emph{MP3 player} brainstorming task.

\begin{figure}[!h]
    \begin{enumerate}
        \item "Use as a mirror"
        \item "Mirror"
        \item "Use it as a mirror for makeup"
        \item "Tape it to a telephone pole and use as a reflector"
    \end{enumerate}
    \label{sample_instances}
\end{figure}

@@

The clustering algorithm is described in Figure~\ref{fig:cluseringalg}. Instances are added one at a time to the existing idea forest. In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

@@

As our measure of originality, we use \emph{o-score}, introduced by Jansson and Smith \cite{jansson_design_1991}. An idea's o-score is $1 - p(idea)$, where $p(idea) = (number of instances of that idea)/(number of instances total)$. We similarly calculate o-score for categories. Throughout this paper, we will occasionally refer to the \emph{category o-score} of an idea. This simply refers to the o-score of the category tree to which that idea belongs.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{idea_height}
    \label{idea_height}
\end{figure}

### 2013-09-16 chi2014/related.tex
citations and some figure markup

% TODO Note: I plaigarized the wording on these definitions from wikipedia at this point, should pull from original Osborne at some point
Brainstorming was originally proposed in XXXX by Osborne [CITE]. Brainstorming makes several recommendations for idea generation in groups, the core of which are a set of four rules: \emph{focus on quantity}, \emph{withhold criticism}, \emph{welcome unusual ideas}, and \emph{combine and improve ideas}.

Since then, brainstorming as proposed by Osborne has been extensively evaluated. Very quickly, Taylor et. al established that \emph{nominal groups}, or individuals brainstorming in isolated whose ideas are later combined, performed better than real groups in terms of number of ideas generated [CITE]. Furthermore, Diehl and Stroebe found extremely high correlation (XX) between the number of ideas generated and the quality of ideas, a finding that has been verified many times since (Another citation here would be nice). In Bouchard and Hare [CITE], nominal brainstorming groups were able to generate quantities of ideas linear in the number of members in the group.

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network. Participants can enter ideas while simultaneously viewing the ideas of all other ideas, anonymously presented on-screen. Gallupe [CITE] found that electronic brainstorming reduced the inhibiting social effects of \emph{production blocking} (the inability for multiple people to speak at once), and \emph{evaluation apprehension} (the fear of judgment) in comparison to in-person groups. However, Pinsonneault et al identify four productivity impediments introduced by group electronic brainstorming, and show that there is little evidence to support the proposition that electronic brainstorming out-performs nominal brainstorming [CITE].

@@

This choice is supported by other users of crowd marketplaces for idea generation. Yu and Nickerson use many individuals in an evolutionary algorithm to generate creative chair designs [CITE]. This technique is compared to single participants generating single ideas, but no baseline is established for idea generators individually exhausting a design space.

@@

% TODO: part of this is Pao-exact, assuming it's cool because she's going to be an author on the paper
While there are no models of nominal brainstorming in the context of a crowd marketplace, several researchers have modelled the idea generation process for individuals and groups. We emphasize the former for its applicability to nominal groups. Nijstad and Stroebe define the \emph{search for ideas in associative memory} (SIAM) model. SIAM assumes two stages of idea generation: knowledge activation based on search of working memory, and idea production within a single activated image. This model verifies three predictions for individual brainstorming behaviour:

>>>>

% TODO Note: I plaigarized the wording on these definitions from wikipedia at this point, should pull from original Osborne at some point
Brainstorming was originally proposed in XXXX by Osborne \cite{osborn_applied_1957}. Brainstorming makes several recommendations for idea generation in groups, the core of which are a set of four rules: \emph{focus on quantity}, \emph{withhold criticism}, \emph{welcome unusual ideas}, and \emph{combine and improve ideas}.

Since then, brainstorming as proposed by Osborne has been extensively evaluated. Very quickly, Taylor et. al established that \emph{nominal groups}, or individuals brainstorming in isolated whose ideas are later combined, performed better than real groups in terms of number of ideas generated \cite{taylor_does_1958}. Furthermore, Diehl and Stroebe found that groups which generated good ideas also generated many ideas \cite{diehl_productivity_1987}, a finding that has been verified many times since (Another citation here would be nice). In Bouchard and Hare \cite{bouchard_jr_size_1970}, nominal brainstorming groups were able to generate quantities of ideas linear in the number of members in the group.

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network. Participants can enter ideas while simultaneously viewing the ideas of all other ideas, anonymously presented on-screen. Gallupe \cite{gallupe_electronic_1992} found that electronic brainstorming reduced the inhibiting social effects of \emph{production blocking} (the inability for multiple people to speak at once), and \emph{evaluation apprehension} (the fear of judgment) in comparison to in-person groups. However, Pinsonneault et al identify four productivity impediments introduced by group electronic brainstorming, and show that there is little evidence to support the proposition that electronic brainstorming out-performs nominal brainstorming \cite{pinsonneault_electronic_1999}.

@@

This choice is supported by other users of crowd marketplaces for idea generation. Yu and Nickerson use many individuals in an evolutionary algorithm to generate creative chair designs \cite{yu_cooks_2011}. This technique is compared to single participants generating single ideas, but no baseline is established for idea generators individually exhausting a design space.

@@

% TODO: part of this is Pao-exact, assuming it's cool because she's going to be an author on the paper
While there are no models of nominal brainstorming in the context of a crowd marketplace, several researchers have modelled the idea generation process for individuals and groups. We emphasize the former for its applicability to nominal groups. Nijstad and Stroebe define the \emph{search for ideas in associative memory} (SIAM) model \cite{nijstad_how_2006}. SIAM assumes two stages of idea generation: knowledge activation based on search of working memory, and idea production within a single activated image. This model verifies three predictions for individual brainstorming behaviour:
